---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r, echo=TRUE}
library(ggplot2)
library(scales)

```

## Loading and preprocessing the data
```{r, echo=TRUE}

if(!file.exists('activity.csv')){
  unzip('activity.zip')
}
activity <- read.csv('activity.csv')
```
# 2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r, echo = TRUE}
activity$date <- as.Date(activity$date, format = "%Y-%m-%d")
activity$interval <- as.factor(activity$interval)
```
## What is mean total number of steps taken per day?
```{r, echo=TRUE}
stepsByDay <- tapply(activity$steps, activity$date, sum, na.rm=TRUE)
```

# 1. Make a histogram of the total number of steps taken each day
```{r}
qplot(stepsByDay, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```
## 2. Calculate and report the mean and median total number of steps taken per day
```{r}
stepsByDayMean <- mean(stepsByDay)
stepsByDayMedian <- median(stepsByDay)
```
* Mean: `r stepsByDayMean`
* Median:  `r stepsByDayMedian`


## What is the average daily activity pattern?

```{r}
averageStepsPerTimeBlock <- aggregate(x=list(meanSteps=activity$steps), by=list(interval=activity$interval), FUN=mean, na.rm=TRUE)
```

## 1. Make a time series plot
```{r}
ggplot(data=averageStepsPerTimeBlock, aes(x=interval, y=meanSteps)) +
    geom_line() +
    xlab("5-minute interval") +
   ylab("average number of steps taken") 
```
## 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
mostSteps <- which.max(averageStepsPerTimeBlock$meanSteps)
timeMostSteps<-  gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", averageStepsPerTimeBlock[mostSteps,'interval'])
```
 
* Most Steps at: `r timeMostSteps`


## Imputing missing values
## 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
numMissingValues <- length(which(is.na(activity$steps)))
```

* Number of missing values: `r numMissingValues`
 
## 2. Devise a strategy for filling in all of the missing values in the dataset.
## 3. Create a new dataset that is equal to the original dataset but with the #missing data filled in.
#```{r}
#activityImputed <- activity

#
#```
 
### 4. Make a histogram of the total number of steps taken each day 
#```{r}
#stepsByDayImputed <- tapply(activityDataImputed$steps, activityDataImputed$date, #sum)
#qplot(stepsByDayImputed, xlab='Total steps per day (Imputed)', ylab='Frequency #using binwith 500', binwidth=500)
#```## ... and Calculate and report the mean and median total number of steps #taken per day. 





## Are there differences in activity patterns between weekdays and weekends?
